\documentclass[10pt,a4paper,ragged2e]{altacv}
\geometry{left=2cm,right=10cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm}

\ifxetexorluatex
  \setmainfont{Carlito}
\else
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage[default]{lato}
\fi

\definecolor{VividPurple}{HTML}{000000}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{2E2E2E}
\colorlet{heading}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

\addbibresource{sample.bib}

\usepackage[czech]{babel}
\usepackage{csquotes}

\begin{document}
\name{Milan Veselý}
\tagline{Software Engineer at Pure Storage and Computer Science student at Matfyz}
% Cropped to square from https://en.wikipedia.org/wiki/Marissa_Mayer#/media/File:Marissa_Mayer_May_2014_(cropped).jpg, CC-BY 2.0
%\photo{3.3cm}{profile.jpg}
\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \email{vesely202@gmail.com}
  \phone{+420 730 906 637}
  \github{github.com/vesmil}
  \linkedin{linkedin.com/in/milan-vesely/}
%  \orcid{orcid.org/0000-0000-0000-0000} % Obviously making this up too. If you want to use this field (and also other academicons symbols), add "academicons" option to \documentclass{altacv}
}

\begin{fullwidth}
\makecvheader
\end{fullwidth}

\AtBeginEnvironment{itemize}{\small}

\cvsection[page1sidebar]{Introduction} I am currently enrolled as a first-year student in the Software Systems master's degree program at Charles University. At the same time I am also working full-time as a software engineer at Pure Storage.

\vspace{4px}

Throughout my Bachelor studies, I have gained practical experience working with companies of various sizes, mostly specializing in C++ development. Despite juggling work and studies, I have maintained an outstanding academic record, I have been repeatedly recognized with scholarships for excellent results and even graduated with honors.

\vspace{4px}

I enjoy problem solving and learning new things, but I don't neglect other important skills such TODO...

\vspace{8px}

\cvsection{Education}

\cvevent{Bachelor in Computer Science}{Charles University}{2020 -- 2023}{Prague}

\cvevent{Masters in Computer Science}{Charles University}{2023 -- now}{Prague}

\vspace{8px}

\cvsection{Extracurricular}

\textbf{Programming Teacher, Code Rebels}

\vspace{2px}

\begin{itemize}
\item Develop and deliver Python courses for kids, focusing on programming fundamentals, algorithms, and problem-solving.
\end{itemize}

\vspace{4px}

\textbf{High School Technical Competitions}

\vspace{2px}

\begin{itemize}
\item Awarded numerous medals for performance in Mathematical Olympiad, Logical Olympiad, and other technical competitions.
\item Demonstrated strong problem-solving skills and a passion for learning and applying mathematical and logical concepts.
\end{itemize}

\vspace{4px}

\textbf{Event Organizer}

\vspace{2px}

\begin{itemize}
\item Led teams of 5 or more to organize cultural and sporting events for hundreds of people, such as muggle quidditch tournament, ice-hockey matches, concerts, and more.
\end{itemize}

\vspace{8px}

\cvsection{Abilities}
%\divider

% \divider

\cvskill{ C++}{4}
\cvskill{ C\#}{3}
\cvskill{ Python }{2}

\vspace{10px} \ And others such as Git, Linux, Scrum, LaTeX, ...

\vspace{10px} \textit{*The rating is mostly relative}

\clearpage

\nocite{*}

% \printbibliography[heading=pubtype,title={\printinfo{\faBook}{Books}},type=book]

% \divider

% \printbibliography[heading=pubtype,title={\printinfo{\faFileTextO}{Journal Articles}}, type=article]

% \divider

% \printbibliography[heading=pubtype,title={\printinfo{\faGroup}{Conference Proceedings}},type=inproceedings]

% %% If the NEXT page doesn't start with a \cvsection, but you'd
% %% still like to add a sidebar, then use this command on THIS
% %% page to add it. The optional argument lets you pull up the
% %% sidebar a bit so that it looks aligned with the top of the
% %% main column.
% % \addnextpagesidebar[-1ex]{page3sidebar}

\end{document}
